---
title: "MAS467 Project. Synopsis"
output: html_notebook
---
# Insralling and loading libraries
```{r}
install.packages("ggplot2")
install.packages("RcppArmadillo")
install.packages("minerva")
install.packages("energy")
```
```{r}
library(ggplot2)
library(minerva)
library(gridExtra)
library(stats)
library(energy)
library(tidyr)
```

# Testing the minerva package
```{r}
x <- 0:200 / 200
y <- sin(10 * pi * x) + x
mine(x,y, n.cores=1)
```

```{r}
x <- 0:200 / 200
y <- sin(10 * pi * x) + x
mine_stat(x, y, measure="mic")
```

# Loading the data for simulations
## Cubic nullcline simulations
```{r}
setwd("simulation/data_cubic_nullcline")
csv_files <- list.files(pattern = "\\.csv$")
cubic_nullcline <- list()

cubic_nullcline <- lapply(csv_files, function(file) {
  df_name <- sub(".csv", "", file)  # Remove the ".csv" extension
  read.csv(file, sep = ";", header = TRUE)
})
names(cubic_nullcline) <- sapply(cubic_nullcline, function(df) deparse(substitute(df)))
```
## Apoptosis model simulations
```{r}
setwd("simulation/data_apoptosis")
csv_files <- list.files(pattern = "\\.csv$")
apoptosis <- list()

apoptosis <- lapply(csv_files, function(file) {
  df_name <- sub(".csv", "", file)  # Remove the ".csv" extension
  read.csv(file, sep = ";", header = TRUE)
})
names(apoptosis) <- sapply(apoptosis, function(df) deparse(substitute(df)))
```

## Simple datasets

```{r}
relationships <- c("positive_linear", "negative_linear", "no_relationship", "polynomial", "sinusoidal", "ellipsoid", "circular", "spiral")
relationship_datasets <- list()

# Set the common parameters
set.seed(123)  # For reproducibility
n <- 1000       # Number of data points
x <- seq(0, 10, length.out = n)  # X values
noise_levels <- seq(0, 1, length.out = 101)

# Function to adjust noise based on R^2
adjust_noise <- function(y, x, desired_R2) {
  y_baseline <- y
  lm_baseline <- lm(y_baseline ~ x)
  R2_baseline <- summary(lm_baseline)$r.squared
  
  sd_initial <- sd(y) * 0.5
  for (i in 1:100) {  # Max 100 iterations
    noise <- rnorm(length(y), 0, sd_initial)
    y_noisy <- y_baseline + noise
    lm_noisy <- lm(y_noisy ~ x)
    R2_noisy <- summary(lm_noisy)$r.squared
    
    if (abs(R2_noisy - desired_R2) < 0.001) {
      break
    } else {
      if (R2_noisy < desired_R2) {
        sd_initial <- sd_initial * 0.9  # Adjust noise
      } else {
        sd_initial <- sd_initial * 1.1  # Adjust noise
      }
    }
  }
  return(y_noisy)
}

# Function to generate circular data in polar coordinates
generate_circular_data <- function(n_points, noise_level) {
  theta <- seq(0, 2 * pi, length.out = n_points)
  r <- rep(1, n_points)  # You can adjust the radius as needed
  noise <- rnorm(n_points, 0, noise_level)
  return(data.frame(x = (r + noise) * cos(theta), y = (r + noise) * sin(theta)))
}

# Function to generate spiral data in polar coordinates
generate_spiral_data <- function(n_points, noise_level) {
  theta <- seq(0, 4 * pi, length.out = n_points)
  r <- 0.5 * theta  # Adjust the factor to control the spiral shape
  noise <- rnorm(n_points, 0, noise_level)
  return(data.frame(x = (r + noise) * cos(theta), y = (r + noise) * sin(theta)))
}


# Create and save datasets based on the relationship
for (relationship in relationships) {
  cat("Generating datasets for:", relationship, "\n")
  relationship_data <- list()  # To store datasets for this relationship

  for (noise in noise_levels) {
    if (relationship == "positive_linear") {
      y <- 2 * x + 1
    } else if (relationship == "negative_linear") {
      y <- -2 * x + 1
    } else if (relationship == "no_relationship") {
      y <- rep(5, n)
    } else if (relationship == "polynomial") {
      y <- 0.5 * x^2 - 1
    } else if (relationship == "sinusoidal") {
      y <- sin(x) + cos(x)
      # Directly add noise based on noise level
      noise_stddev <- noise * (max(y) - min(y))
      y <- y + rnorm(length(y), 0, noise_stddev)
    } else if (relationship == "ellipsoid") {
      a <- 3
      b <- 2
      x_center <- 5
      y_center <- 5
      y <- y_center + b * sqrt(1 - ((x - x_center) / a)^2)
      # Directly add noise based on noise level
      noise_stddev <- noise * (max(y, na.rm = TRUE) - min(y, na.rm = TRUE))
      y <- y + rnorm(length(y), 0, noise_stddev)
      # Remove NaN values for ellipsoid
      nan_rows <- is.na(y)
      x <- x[!nan_rows]
      y <- y[!nan_rows]
    } else if (relationship == "circular") {
      data <- generate_circular_data(n, noise)
      x <- data$x
      y <- data$y
    } else if (relationship == "spiral") {
      data <- generate_spiral_data(n, noise)
      x <- data$x
      y <- data$y
    }
    if (relationship == "no_relationship") {
      y_noisy <- y + rnorm(n, mean = 0, sd = noise) # Add noise directly without R^2 adjustment
    } else {
      y_noisy <- adjust_noise(y, x, 1-noise)
    }
    relationship_data[[as.character(noise)]] <- data.frame(x = x, y = y_noisy)
  }

  relationship_datasets[[relationship]] <- relationship_data
}


```

```{r}
setwd("simulation/noisy_cubic")
csv_files <- list.files(pattern = "\\.csv$")
noisy_cubic <- list()

noisy_cubic <- lapply(csv_files, function(file) {
  df_name <- sub("\\.csv", "", file)  # Remove the ".csv" extension
  df <- read.csv(file, sep = ";", header = TRUE)
  df[, !grepl("^t$", names(df))]
})
# Multiply each number by 10 when assigning names to the list elements
names(noisy_cubic) <- as.character(as.numeric(sub("\\.csv", "", csv_files)) * 10)
```
```{r}
relationship_datasets[["ODE"]] <- noisy_cubic
relationships <- c(relationships, "ODE")
```

## Visualizing simulated datasets
```{r}
# Function to visualize datasets
visualize_datasets <- function(relationship_datasets) {
  par(mfrow = c(2, 3))  # Arrange plots in a 2x3 grid
  for (relationship in names(relationship_datasets)) {
    cat("Visualizing datasets for:", relationship, "\n")

    relationship_data <- relationship_datasets[[relationship]]
    noise_levels <- names(relationship_data)
    desired_levels <- c(0, 0.1, 0.25, 0.5, 0.75, 1)

    # Use the %in% operator to filter the desired noise levels
    noise_levels <- noise_levels[noise_levels %in% desired_levels]
    ggplot_list <- list()
    for (i in seq_along(noise_levels)) {
      dataset <- relationship_data[[noise_levels[i]]]
      noise <- noise_levels[i]
      main_title <- paste(relationship, "with noise =", noise)

      # Create a ggplot and store it in the list
      p <- ggplot(dataset, aes(x, y)) +
        geom_line(color = "blue") +
        labs(title = main_title)
      ggplot_list[[i]] <- p
    }

    # Arrange the ggplots in a grid and save as a PNG image
    grid_arrange = grid.arrange(grobs = ggplot_list, ncol = 2)  # 2 plots per row

    # Save the grid as a PNG image with the specified title
    grid_filename <- paste("plots/", gsub(" ", "_", relationship), "_grid.png", sep = "")
    ggsave(grid_filename, plot = grid_arrange, width = 12, height = 8, dpi = 300)
  }
}

# Call the function to visualize the datasets
visualize_datasets(relationship_datasets)
```


# Testing MIC
## Testing simple simulations 
```{r}
# Create a data frame to store results
results_2 <- data.frame(NoiseLevel = numeric(0), MINE = numeric(0), RelationshipType = character(0))

# Loop through the relationship datasets
for (i in 1:length(relationship_datasets)) {
  relationship_data <- relationship_datasets[[i]]
  noise_levels <- names(relationship_data)
  for (j in noise_levels){
    #print(j)
    #print(relationships[i])
    mic_values <- mine_stat(relationship_data[[j]]$x, 
                       relationship_data[[j]]$y,
                       measure='mic')
    
    # Create a data frame for this relationship type
    relationship_type <- rep(relationships[i], length(noise_levels))
    df <- data.frame(NoiseLevel = j, MINE = mic_values, RelationshipType = relationship_type)
    
    # Append the results to the main data frame
    results_2 <- rbind(results_2, df)
    }}
```
## Visualizing simple simulations 
```{r}
results_2$NoiseLevel <- as.factor(results_2$NoiseLevel)

p <- ggplot(results_2, aes(x = NoiseLevel, y = MINE, color = RelationshipType)) +
  geom_jitter(width = 0.0002, height = 0.0002)  +
  scale_x_discrete(breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = c("0", "0.2", "0,4", "0.6", "0.8", "1")) +
  labs(x = "Noise Level", y = "MIC Value") +
  scale_color_discrete(name = "Relationship Type", 
                       labels = function(x) gsub("_", " ", x)) + # Replacing underscores with spaces
  theme_minimal()
p

ggsave("TestDataMIC.png", plot = p, dpi = 300)
```
## Computing Dist. Corr. for the same datasets
```{r}
# Create a data frame to store results
results_ener <- data.frame(NoiseLevel = numeric(0), dcor = numeric(0), RelationshipType = character(0))

# Loop through the relationship datasets
for (i in 1:length(relationship_datasets)) {
  relationship_data <- relationship_datasets[[i]]
  noise_levels <- names(relationship_data)
  for (j in noise_levels){
    #print(j)
    #print(relationships[i])
    dcor_values <- dcor(relationship_data[[j]]$x, 
                       relationship_data[[j]]$y)
    
    # Create a data frame for this relationship type
    relationship_type <- rep(relationships[i], length(noise_levels))
    df <- data.frame(NoiseLevel = j, dcor = dcor_values, RelationshipType = relationship_type)
    
    # Append the results to the main data frame
    results_ener <- rbind(results_ener, df)
    }}
```
## Visualizing Dist. Corr. results
```{r}
results_ener$NoiseLevel <- as.factor(results_ener$NoiseLevel)

p <- ggplot(results_ener, aes(x = NoiseLevel, y = dcor, color = RelationshipType)) +
  geom_jitter(width = 0.0002, height = 0.0002)  +
  scale_x_discrete(breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = c("0", "0.2", "0,4", "0.6", "0.8", "1")) +
  labs(x = "Noise Level", y = "Dist. Corr. Value") +
  scale_color_discrete(name = "Relationship Type", 
                       labels = function(x) gsub("_", " ", x)) + # Replacing underscores with spaces
  theme_minimal()
p

ggsave("TestDataDistCorr.png", plot = p, dpi = 300)
```
# Applying radial transformation

```{r}
# Function to convert Cartesian coordinates to polar coordinates
cartesian_to_polar <- function(x, y) {
  r <- sqrt(x^2 + y^2)
  theta <- atan2(y, x)
  return(data.frame(r = r, theta = theta))
}

# Create and save datasets based on the relationship in polar coordinates
relationship_datasets_radial <- list()

for (relationship in relationships) {
  cat("Generating datasets for:", relationship, "in radial coordinates\n")
  relationship_data_radial <- list()  # To store datasets in radial coordinates for this relationship

  for (noise in noise_levels) {
    # Retrieve Cartesian coordinates from the original datasets
    cartesian_data <- relationship_datasets[[relationship]][[as.character(noise)]]
    
    # Convert Cartesian to polar coordinates
    polar_data <- cartesian_to_polar(cartesian_data$x, cartesian_data$y)
    
    relationship_data_radial[[as.character(noise)]] <- polar_data
  }

  relationship_datasets_radial[[relationship]] <- relationship_data_radial
}
```

## Testing simple simulations 
```{r}
# Create a data frame to store results
results_2 <- data.frame(NoiseLevel = numeric(0), MINE = numeric(0), RelationshipType = character(0))

# Loop through the relationship datasets
for (i in 1:length(relationship_datasets_radial)) {
  relationship_data <- relationship_datasets_radial[[i]]
  noise_levels <- names(relationship_data)
  
  for (j in noise_levels){
    #print(j)
    #print(relationships[i])
    mic_values <- mine_stat(relationship_data[[j]]$r, 
                       relationship_data[[j]]$theta,
                       measure='mic')
    
    # Create a data frame for this relationship type
    relationship_type <- rep(relationships[i], length(noise_levels))
    df <- data.frame(NoiseLevel = j, MINE = mic_values, RelationshipType = relationship_type)
    
    # Append the results to the main data frame
    results_2 <- rbind(results_2, df)
    }}
```
## Visualizing simple simulations 
```{r}
results_2$NoiseLevel <- as.factor(results_2$NoiseLevel)

p <- ggplot(results_2, aes(x = NoiseLevel, y = MINE, color = RelationshipType)) +
  geom_jitter(width = 0.0002, height = 0.0002)  +
  scale_x_discrete(breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = c("0", "0.2", "0,4", "0.6", "0.8", "1")) +
  labs(x = "Noise Level", y = "MIC Value") +
  scale_color_discrete(name = "Relationship Type", 
                       labels = function(x) gsub("_", " ", x)) + # Replacing underscores with spaces
  theme_minimal()
p

ggsave("TestDataMICPolar.png", plot = p, dpi = 300)
```
## Computing Dist. Corr. for the same datasets
```{r}
# Create a data frame to store results
results_ener <- data.frame(NoiseLevel = numeric(0), dcor = numeric(0), RelationshipType = character(0))

# Loop through the relationship datasets
for (i in 1:length(relationship_datasets_radial)) {
  relationship_data <- relationship_datasets_radial[[i]]
  noise_levels <- names(relationship_data)
  for (j in noise_levels){
    #print(j)
    #print(relationships[i])
    dcor_values <- dcor(relationship_data[[j]]$r, 
                       relationship_data[[j]]$theta)
    
    # Create a data frame for this relationship type
    relationship_type <- rep(relationships[i], length(noise_levels))
    df <- data.frame(NoiseLevel = j, dcor = dcor_values, RelationshipType = relationship_type)
    
    # Append the results to the main data frame
    results_ener <- rbind(results_ener, df)
    }}
```
## Visualizing Dist. Corr. results
```{r}
results_ener$NoiseLevel <- as.factor(results_ener$NoiseLevel)

p <- ggplot(results_ener, aes(x = NoiseLevel, y = dcor, color = RelationshipType)) +
  geom_jitter(width = 0.0002, height = 0.0002)  +
  scale_x_discrete(breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = c("0", "0.2", "0,4", "0.6", "0.8", "1")) +
  labs(x = "Noise Level", y = "Dist. Corr. Value") +
  scale_color_discrete(name = "Relationship Type", 
                       labels = function(x) gsub("_", " ", x)) + # Replacing underscores with spaces
  theme_minimal()
p

ggsave("TestDataDistCorrPolar.png", plot = p, dpi = 300)
```

## Testing the systems biology datasets
### Cubic nuclines
```{r}
mic_scores <- c()
for (df in cubic_nullcline) {
  mic <- mine_stat(df$x, df$y, measure = 'mic')
  mic_scores <- c(mic_scores, mic)
}
```

```{r}
# Create a horizontal box plot
p <- ggplot(data = data.frame(MIC_Score = mic_scores), aes(x = MIC_Score)) +
  geom_boxplot() +
  labs(x = "MIC Score", y = NULL) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),    # Remove y-axis text (labels)
        axis.ticks.y = element_blank())
p
ggsave("CubicNullclineMIC.png", plot = p, width=6, height = 2, dpi = 300)

```
### Apoptosis 
```{r}
mic_scores_list <- list()
variable_names <- colnames(apoptosis[[1]])
variable_names <- variable_names[variable_names != "t"]

n_random_elements <- 10
random_indices <- sample(length(apoptosis), n_random_elements)
reduced_apoptosis <- apoptosis[random_indices]

# Iterate through each dataframe in the list
for (i in 1:length(reduced_apoptosis)) {
  df <- reduced_apoptosis[[i]]
  
  # Initialize an empty matrix to store the MIC scores for this dataframe
  mic_matrix <- matrix(NA, ncol = 8, nrow = 8)
  colnames(mic_matrix) <- variable_names
  rownames(mic_matrix) <- variable_names
  
  # Iterate through all combinations of variable pairs
  for (var1 in 1:7) {
    for (var2 in (var1 + 1):8) {
      
      # Calculate the MIC score using the mine_stat function
      mic_score <- mine_stat(df[[variable_names[var1]]], 
                             df[[variable_names[var2]]], 
                             measure = 'mic')
      print(mic_score)
      # Store the MIC score in the matrix
      mic_matrix[variable_names[var1], variable_names[var2]] <- mic_score
      mic_matrix[variable_names[var2], variable_names[var1]] <- mic_score
    }
  }
  
  # Append the MIC scores matrix to the list
  mic_scores_list[[i]] <- mic_matrix
}

# Now, mic_scores_list contains the MIC scores for all variable pairs in each dataframe

```
```{r}
# Create an empty data frame
# Create an 8x8 matrix of empty lists
list_matrix <- matrix(vector("list", 64), nrow = 8)

# Now, for each matrix in your list, we will go through every element in the matrix 
# and append it to the corresponding list in the list_matrix.
for (mat in mic_scores_list) {
  for (i in 1:8) {
    for (j in 1:8) {
      list_matrix[[i, j]] <- c(list_matrix[[i, j]], mat[i, j])  # Append elements
    }
  }
}

# Convert the list_matrix into a data frame. Each cell of this data frame contains a list.
comb_df <- as.data.frame(list_matrix)

# Naming the rows and columns as per the original matrix
rownames(comb_df) <- colnames(mic_scores_list[[1]]) # assuming all matrices have the same column names
colnames(comb_df) <- colnames(mic_scores_list[[1]])

```


```{r}
# Assuming 'df' is your 8x8 data frame from the previous step

# Create an empty list to store the data for plotting
plot_data <- list()

# A function to generate a unique key for each pair of variables
# to ensure we don't duplicate var1-var2 and var2-var1
make_key <- function(var1, var2) {
  return(paste(sort(c(var1, var2)), collapse = "-"))
}

# Used to keep track of the keys we've added
keys <- c()

# Extract data for the box plots
for (i in 1:8) {
  for (j in 1:8) {
    if (i != j) {  # Avoid entries with the same variable
      key <- make_key(rownames(comb_df)[i], colnames(comb_df)[j])

      if (!key %in% keys) {  # Avoid adding the same combination of variables
        keys <- c(keys, key)

        # Create a data frame for each pair for ggplot compatibility, store in list
        plot_data[[key]] <- data.frame(
          value = unlist(comb_df[i, j], use.names = FALSE),
          pair = key
        )
      }
    }
  }
}

# Combine all the data frames for ggplot
combined_data <- do.call(rbind, plot_data)


```

```{r}

# Create the box plot
p <- ggplot(combined_data, aes(x = pair, y = value)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  # Rotate x-axis labels for readability
  labs(title = "Apoptosis Simulation MIC (n=50)",
       x = "Variable Pair",
       y = "MIC")

p

ggsave("ApoptosisMIC.png", plot = p, dpi = 300)

```

```{r}
n_random_elements <- 1
random_indices <- sample(length(apoptosis), n_random_elements)
reduced_apoptosis <- apoptosis[random_indices]

# Assuming your list of dataframes is named 'reduced_apoptosis' and 'mine' function is already defined

# Step 1: Apply the 'mine' function to each dataframe in the list and each column in the dataframes

# Initialize a list to hold the results. Each element of the list will be a vector of results from 'mine' function
results_list <- list()

# y is a vector of constant value with small random noise
# Here, we're generating a sample y. You should replace this with your actual y values.
set.seed(123) # for reproducibility of random numbers


# Loop through each dataframe
for (i in seq_along(reduced_apoptosis)) {
  df <- reduced_apoptosis[[i]]  # get the current dataframe
  num_rows <- nrow(reduced_apoptosis[[i]])
  y <- 1 + sapply(1:num_rows, function(x) rnorm(1, mean = 0, sd = 0.1))
  # This function checks if 'mine' is applicable, then applies 'mine' for each column against 'y'.
  results <- sapply(df[, names(df) != "t"], function(x) {
    
    if (length(x) == length(y)) {
      mine_result <- mine_stat(x, y, measure='mic')  
      return(mine_result)
    } else {
      stop("Length of 'x' and 'y' do not match")
    }
  })

  results_list[[i]] <- results  # store the results
}

# Step 2: Rearrange the data for plotting

# Since you have 8 variables (excluding 't'), we create an empty data frame to hold the results for plotting
plot_data <- data.frame(variable = character(), value = numeric(), stringsAsFactors = FALSE)

# Now we populate 'plot_data' with the results, along with the corresponding variable name
for (var_index in 1:8) { # assuming 8 variables excluding 't'
  for (list_index in seq_along(results_list)) {
    temp_df <- data.frame(
      variable = paste0("Var", var_index),
      value = results_list[[list_index]][var_index, ], # extracting results for the current variable
      stringsAsFactors = FALSE
    )
    plot_data <- rbind(plot_data, temp_df) # appending to the plot data
  }
}

# Step 3: Plotting

# Now using ggplot to create a boxplot
ggplot(plot_data, aes(x = variable, y = value)) +
  geom_boxplot() +
  labs(title = "Results of 'mine' function across variables", x = "Variable", y = "mine function output") +
  theme_minimal()

```


```{r}
mic_scores_list <- list()
variable_names <- colnames(apoptosis[[1]])
variable_names <- variable_names[variable_names != "t"]
n_random_elements <- 7
random_indices <- sample(length(apoptosis), n_random_elements)
reduced_apoptosis <- apoptosis[random_indices]
answer <- data.frame(matrix(ncol = 8, nrow = 0))
colnames(answer) <- variable_names
```
```{r}

# Iterate through each dataframe in the list

for (i in 1:length(reduced_apoptosis)) {
  df <- reduced_apoptosis[[i]]
  num_rows <- nrow(reduced_apoptosis[[i]])
  y <- 1 + sapply(1:num_rows, function(x) rnorm(1, mean = 0, sd = 0.1))
  # Initialize an empty matrix to store the MIC scores for this dataframe
  new_row <- c()
  print('loh')
  # Iterate through all combinations of variable pairs
  for (var1 in 1:8) {
    # Calculate the MIC score using the mine_stat function
    mic_score <- mine_stat(df[[variable_names[var1]]], 
                           y, 
                           measure = 'mic')
    # Store the MIC score in the matrix
    new_row <- c(new_row, mic_score)
  }
  
  # Append the MIC scores matrix to the list
  answer <- rbind(answer, new_row)
}

# Now, mic_scores_list contains the MIC scores for all variable pairs in each dataframe

```

```{r}
colnames(answer) <- variable_names
long_data <- pivot_longer(answer, cols = everything(), names_to = "Column", values_to = "Value")

# Plotting
p <- ggplot(long_data, aes(x = Column, y = Value)) +
  geom_boxplot() +
  labs(title = "Boxplot against random noise", y = "MIC Value") +
  xlab(NULL) +
  facet_wrap(~ Column, scales = "free")

p

ggsave("ApoptosisMIC_Rand.png", plot = p, dpi = 300)

```

# Stochastic Model Analysis

```{r}
setwd("simulation/stochastic")
csv_files <- list.files(pattern = "\\.csv$")
stochastic <- list()

stochastic <- lapply(csv_files, function(file) {
  df_name <- sub(".csv", "", file)  # Remove the ".csv" extension
  df <- read.csv(file, sep = ",", header = TRUE)
  colnames(df) <- c("x", "y")
  return(df)
})
names(stochastic) <- sapply(stochastic, function(df) deparse(substitute(df)))
```

```{r}
n <- 20
random_stochastic <- sample(stochastic, n)
```

```{r}
mic_scores <- c()
i <- 0
for (df in random_stochastic) {
  mic <- mine_stat(df$x, df$y, measure = 'mic')
  mic_scores <- c(mic_scores, mic)
  i <- i + 1
  print(i)
}
```

```{r}
# Create a horizontal box plot
p <- ggplot(data = data.frame(MIC_Score = mic_scores), aes(x = MIC_Score)) +
  geom_boxplot() +
  labs(x = "Stochastic MIC Score", y = NULL) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),    # Remove y-axis text (labels)
        axis.ticks.y = element_blank())
p
ggsave("Stochastic.png", plot = p, width=6, height = 2, dpi = 300)

```
